---
title: "Analysis"
author: "Tom Mushkat"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
editor: visual
---

```{r,warning=FALSE,message=FALSE}

pacman::p_load(here, doSPSS, skimr, tidyverse, psych, ez)

Data <- read_csv(here("Data\\data_to_analyze.csv"))

```

# METI

```{r,warning=FALSE,message=FALSE}

doSPSS_model <- oneWayAnova(Data$METI_overall, Data$Condition)



ezANOVA_no_cov <- 
ezANOVA(data = Data, wid = prolific_ID, dv = METI_overall
        , between = Condition
        , type = '3'
        , return_aov = TRUE)

ezANOVA_with_cov <- 
ezANOVA(data = Data, wid = prolific_ID, dv = METI_overall
        , between = Condition
        , between_covariates = .(val_expert_knowledge)
        , type = '3'
        , return_aov = TRUE)


```

## Descriptive statistics + Figure

In the figure we can see the Mean and the 95% CI.

```{r,warning=FALSE,message=FALSE}
doSPSS_model$Descriptive_Statistics

Data %>% 
    ggplot(aes(x = Condition, y = METI_overall, fill = Condition)) +
geom_violin(alpha = 0) +
   ggplot2::stat_summary(fun.data = "mean_cl_normal", conf.int = .95, geom = "errorbar", color = "red", width = 0.2, size = 1, position = position_dodge(0.9)) +
    ggplot2::stat_summary(fun = mean, geom = "bar", alpha = 0.2, position = position_dodge(0.9)) +
    # ggplot2::ylab('METI')  +
    ggplot2::theme_bw() +
  ylim(1, 10) +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        )
```

## Anova

### Anova without covariates

The model is marginally significant

```{r,warning=FALSE,message=FALSE}
ezANOVA_no_cov$ANOVA
```

### Anova with the validation questions as a covariate

The model is significant

```{r,warning=FALSE,message=FALSE}
ezANOVA_with_cov$ANOVA
```

## Specific contrasts

```{r,warning=FALSE,message=FALSE}
postHoc(Data$METI_overall, Data$Condition)
```

# Expertise

```{r,warning=FALSE,message=FALSE}

doSPSS_model <- oneWayAnova(Data$Expertise, Data$Condition)


ezANOVA_no_cov <- 
ezANOVA(data = Data, wid = prolific_ID, dv = Expertise
        , between = Condition
        , type = '3'
        , return_aov = TRUE)

ezANOVA_with_cov <- 
ezANOVA(data = Data, wid = prolific_ID, dv = Expertise
        , between = Condition
        , between_covariates = .(val_expert_knowledge)
        , type = '3'
        , return_aov = TRUE)


```

## Descriptive statistics + Figure

In the figure we can see the Mean and the 95% CI.

```{r,warning=FALSE,message=FALSE}
doSPSS_model$Descriptive_Statistics

Data %>% 
    ggplot(aes(x = Condition, y = Expertise, fill = Condition)) +
geom_violin(alpha = 0) +
   ggplot2::stat_summary(fun.data = "mean_cl_normal", conf.int = .95, geom = "errorbar", color = "red", width = 0.2, size = 1, position = position_dodge(0.9)) +
    ggplot2::stat_summary(fun = mean, geom = "bar", alpha = 0.2, position = position_dodge(0.9)) +
    # ggplot2::ylab('METI')  +
    ggplot2::theme_bw() +
  ylim(1, 10) +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        )
```

## Anova

### Anova without covariates

The model is marginally significant

```{r,warning=FALSE,message=FALSE}
ezANOVA_no_cov$ANOVA
```

### Anova with the validation questions as a covariate

The model is significant

```{r,warning=FALSE,message=FALSE}
ezANOVA_with_cov$ANOVA
```

## Specific contrasts

This is the multiple pairwise with a correction for p. I also did separate t-tests because we suggested it in the pre-registration. However, the t-tests results did not reveal different results so I did not included them.

As you can see the difference between the two conditions of the IDK is significant, but the differences between the Know and the other IDK is not.

In specific t.tests (non-adjusted p), the p for the IDK_reason-IDK_no_reason comparison is 0.02 and the p for the Know-IDK_reason comparison is 0.09.

```{r,warning=FALSE,message=FALSE}
postHoc(Data$Expertise, Data$Condition)

ezANOVA(data = Data[Data$Condition != 'IDK_no_reason', ], wid = prolific_ID, dv = Expertise
        , between = Condition
        , between_covariates = .(val_expert_knowledge)
        , type = '3'
        , return_aov = TRUE)

ezANOVA(data = Data[Data$Condition != 'IDK_reason', ], wid = prolific_ID, dv = Expertise
        , between = Condition
        , between_covariates = .(val_expert_knowledge)
        , type = '3'
        , return_aov = TRUE)

```

# Integrity

```{r,warning=FALSE,message=FALSE}

doSPSS_model <- oneWayAnova(Data$Integrity, Data$Condition)


ezANOVA_no_cov <- 
ezANOVA(data = Data, wid = prolific_ID, dv = Integrity
        , between = Condition
        , type = '3'
        , return_aov = TRUE)

ezANOVA_with_cov <- 
ezANOVA(data = Data, wid = prolific_ID, dv = Integrity
        , between = Condition
        , between_covariates = .(val_expert_knowledge)
        , type = '3'
        , return_aov = TRUE)


```

## Descriptive statistics + Figure

In the figure we can see the Mean and the 95% CI.

```{r,warning=FALSE,message=FALSE}
doSPSS_model$Descriptive_Statistics

Data %>% 
    ggplot(aes(x = Condition, y = Integrity, fill = Condition)) +
geom_violin(alpha = 0) +
   ggplot2::stat_summary(fun.data = "mean_cl_normal", conf.int = .95, geom = "errorbar", color = "red", width = 0.2, size = 1, position = position_dodge(0.9)) +
    ggplot2::stat_summary(fun = mean, geom = "bar", alpha = 0.2, position = position_dodge(0.9)) +
    # ggplot2::ylab('METI')  +
    ggplot2::theme_bw() +
  ylim(1, 10) +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        )
```

## Anova

### Anova without covariates

The model is significant

```{r,warning=FALSE,message=FALSE}
ezANOVA_no_cov$ANOVA
```

### Anova with the validation questions as a covariate

The model is significant

```{r,warning=FALSE,message=FALSE}
ezANOVA_with_cov$ANOVA
```

## Specific contrasts

```{r,warning=FALSE,message=FALSE}
postHoc(Data$Integrity, Data$Condition)
```

# Benevolence

```{r,warning=FALSE,message=FALSE}

doSPSS_model <- oneWayAnova(Data$Benevolence, Data$Condition)


ezANOVA_no_cov <- 
ezANOVA(data = Data, wid = prolific_ID, dv = Benevolence
        , between = Condition
        , type = '3'
        , return_aov = TRUE)

```

## Descriptive statistics + Figure

In the figure we can see the Mean and the 95% CI.

```{r,warning=FALSE,message=FALSE}
doSPSS_model$Descriptive_Statistics

Data %>% 
    ggplot(aes(x = Condition, y = Benevolence, fill = Condition)) +
geom_violin(alpha = 0) +
   ggplot2::stat_summary(fun.data = "mean_cl_normal", conf.int = .95, geom = "errorbar", color = "red", width = 0.2, size = 1, position = position_dodge(0.9)) +
    ggplot2::stat_summary(fun = mean, geom = "bar", alpha = 0.2, position = position_dodge(0.9)) +
    # ggplot2::ylab('METI')  +
    ggplot2::theme_bw() +
  ylim(1, 10) +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        )
```

## Anova

### Anova without covariates

The model is significant

```{r,warning=FALSE,message=FALSE}
ezANOVA_no_cov$ANOVA
```

## Specific contrasts

```{r,warning=FALSE,message=FALSE}
postHoc(Data$Benevolence, Data$Condition)
```

# Compliance

```{r,warning=FALSE,message=FALSE}

doSPSS_model <- oneWayAnova(Data$Compliance, Data$Condition)


ezANOVA_no_cov <- 
ezANOVA(data = Data, wid = prolific_ID, dv = Compliance
        , between = Condition
        , type = '3'
        , return_aov = TRUE)

```

## Descriptive statistics + Figure

In the figure we can see the Mean and the 95% CI.

```{r,warning=FALSE,message=FALSE}
doSPSS_model$Descriptive_Statistics

Data %>% 
    ggplot(aes(x = Condition, y = Compliance, fill = Condition)) +
geom_violin(alpha = 0) +
   ggplot2::stat_summary(fun.data = "mean_cl_normal", conf.int = .95, geom = "errorbar", color = "red", width = 0.2, size = 1, position = position_dodge(0.9)) +
    ggplot2::stat_summary(fun = mean, geom = "bar", alpha = 0.2, position = position_dodge(0.9)) +
    # ggplot2::ylab('METI')  +
    ggplot2::theme_bw() +
  ylim(1, 10) +
  scale_y_continuous(breaks = seq(from = 1, to = 10, by = 1)) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        )
```

## Anova

### Anova without covariates

The model is significant

```{r,warning=FALSE,message=FALSE}
ezANOVA_no_cov$ANOVA
```

## Specific contrasts

```{r,warning=FALSE,message=FALSE}
postHoc(Data$Compliance, Data$Condition)
```
